---
title: " Impact of marriage pressure on female students on their mental health, education,
and goal-setting."
author: "Analyst -  Ashiqur Rahman Rony"
date: "2023-04-23"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
### Objectives of this study
The mental health of university students is an area of increasing concern 
worldwide. Although some recent studies revealed a high prevalence of depression and 
anxiety among Bangladeshi university students, no study has yet investigated the link 
between marriage pressure and these common psychological disorders and their effects 
on career and goal setup. Therefore, aims of these study is-

- To determine the state of marriage pressure on female undergraduate students
-To determine the association between mental health and marriage pressure.
- To determine how marriage pressure affects education, career, and goal setup.
- To determine the influencing factors behind marriage pressure

### Descriptive Statistics - Frequency analysis
```{r, tbl.align = 'center'}
library(readxl)
data <- read_excel("F:/Fiverr/up-work project/dataset/project 68.xlsx")
tbl<- knitr::kable(table(data$MarriagePressure),col.names = c("Marriage Pressure", "Count"), "simple")
tbl

```






```{r fig, fig.align='center'}

library(plotly)
fig <- plot_ly(data, labels = ~MarriagePressure, values = ~frequency(MarriagePressure), type = 'pie')

fig <- fig %>% layout(title = 'Marriage Pressure of Female Students',
                      
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      width = "50%", 
                      height = 450)

fig

```
A total of 936 participants responded to the survey. Of these, 595 participants answered "No" 
to the question about having marriage pressure, while 341 participants answered "Yes."

The results of the survey indicate that the majority of participants 63.6% answered 
"No" to the question about having marriage pressure. Only 36.4% participants answered "Yes."
This data suggests that a larger proportion of the participants did not experience marriage 
pressure, while a smaller proportion reported that they did. The pie chart provides a clear and 
straightforward representation of the distribution of responses and highlights the differences 
between the two categories.

When we look after another variable PHQ-9 (Patient Health Question) the scores were then 
analyzed to categorize the students into different levels of depression severity, including 
normal depression, mild depression, moderate depression, moderately severe depression, and 
severe depression.

### Depression Severity among students
```{r}
phq_categories<- ifelse(data$phq9 <= 4, "Normal",
       ifelse(data$phq9 <= 9, "Mild", 
              ifelse(data$phq9 <= 14,"Moderate",
                     ifelse(data$phq9 <= 19, "Moderately Severe", 
                            ifelse(data$phq9 <=27,"Severe",data$phq9)))))


phq_categories <- table(phq_categories)
phq_categories_df <- as.data.frame(phq_categories, stringsAsFactors = FALSE)
colnames(phq_categories_df) <- c("Depression Severity", "Frequency")
knitr::kable(phq_categories_df, col.names = c("Depression Severity", "Frequency"), "simple")

library(plotly)
fig <- plot_ly(phq_categories_df, x = ~`Depression Severity`, y = ~Frequency, type = "bar", color = ~`Depression Severity`) %>% 
  layout(title = "Depression Severity Categories", xaxis = list(title = "Category"), yaxis = list(title = "Frequency"))

fig

```



