---
title: " Impact of marriage pressure on female students on their mental health, education,
and goal-setting."
author: "Analyst -  Ashiqur Rahman Rony"
date: This report is made only for showing as a sample project. And the data is manipulated with the real. 
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
### Objectives of this study
The mental health of university students is an area of increasing concern 
worldwide. Although some recent studies revealed a high prevalence of depression and 
anxiety among Bangladeshi university students, no study has yet investigated the link 
between marriage pressure and these common psychological disorders and their effects 
on career and goal setup. Therefore, aims of these study is-

- To determine the state of marriage pressure on female undergraduate students
- To determine the association between mental health and marriage pressure.

### Descriptive Statistics - Frequency analysis
```{r, tbl.align = 'center'}
library(readxl)
data <- read_excel("F:/Fiverr/up-work project/dataset/project 68.xlsx")
tbl<- knitr::kable(table(data$MarriagePressure),col.names = c("Marriage Pressure", "Count"), "simple")
tbl

```






```{r fig, fig.align='center'}

library(plotly)
fig <- plot_ly(data, labels = ~MarriagePressure, values = ~frequency(MarriagePressure), type = 'pie')

fig <- fig %>% layout(title = 'Marriage Pressure of Female Students',
                      
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      width = "50%", 
                      height = 450)

fig

```
A total of 936 participants responded to the survey. Of these, 587 participants answered "No" 
to the question about having marriage pressure, while 349 participants answered "Yes."

The results of the survey indicate that the majority of participants 62.7% answered 
"No" to the question about having marriage pressure. Only 37.3% participants answered "Yes."
This data suggests that a larger proportion of the participants did not experience marriage 
pressure, while a smaller proportion reported that they did. The pie chart provides a clear and 
straightforward representation of the distribution of responses and highlights the differences 
between the two categories.

When we look after another variable PHQ-9 (Patient Health Question) the scores were then 
analyzed to categorize the students into different levels of depression severity, including 
normal depression, mild depression, moderate depression, moderately severe depression, and 
severe depression.

### Depression Severity among students
```{r}
phq_categories<- ifelse(data$phq9 <= 4, "Normal",
       ifelse(data$phq9 <= 9, "Mild", 
              ifelse(data$phq9 <= 14,"Moderate",
                     ifelse(data$phq9 <= 19, "Moderately Severe", 
                            ifelse(data$phq9 <=27,"Severe",data$phq9)))))


phq_categories <- table(phq_categories)
phq_categories_df <- as.data.frame(phq_categories, stringsAsFactors = FALSE)
colnames(phq_categories_df) <- c("Depression Severity", "Frequency")
knitr::kable(phq_categories_df, col.names = c("Depression Severity", "Frequency"), "simple")

library(plotly)
fig <- plot_ly(phq_categories_df, x = ~`Depression Severity`, y = ~Frequency, type = "bar", color = ~`Depression Severity`) %>% 
  layout(title = "Depression Severity Categories", xaxis = list(title = "Category"), yaxis = list(title = "Frequency"))

fig

```

### Marriage Pressure determining by Academic Year


```{r}


tt<-rbind(
  
  
  nrow(data[data$Year == '1st' & data$MarriagePressure == 'yes', ]),
  nrow(data[data$Year == '2nd' & data$MarriagePressure == 'yes', ]),
  nrow(data[data$Year == '3rd' & data$MarriagePressure == 'yes', ]),
  nrow(data[data$Year == '4th' & data$MarriagePressure == 'yes' , ]),
  nrow(data[data$Year == 'masters' & data$MarriagePressure == 'yes', ])
)

academic_yr <- matrix(c('1st','2nd','3rd','4th','masters'), ncol=1)

table_aca<- cbind(academic_yr,tt)

table_aca_df <- as.data.frame(table_aca, stringsAsFactors = FALSE)

# Rename the columns
colnames(table_aca_df) <- c("Academic Year", "Marriage Pressure(yes)")


total_stu<- data.frame(table(data$Year))
colnames(total_stu) <- c("Academic Year", "Marriage Pressure(yes)")

# Merge the two data frames by the "Academic Year" column
merged_df <- merge(table_aca_df, total_stu, by = 'Academic Year' )

knitr::kable(merged_df, col.names = c("Academic Year", "Marriage pressure(yes)", "Total Student"), "simple")
```

The given survey data contains information about the academic year, marriage pressure, and total number of students. Using this data, we created a frequency table and a clustered bar chart to visualize the relationship between academic year, marriage pressure, and total number of students. We also created an interactive stacked bar chart to allow for further exploration of the data. 

```{r}
# Create the bar chart
library(plotly)

plot_ly(merged_df, x = ~merged_df$`Academic Year`, y = ~`Marriage Pressure(yes).x`, name = "Marriage Pressure",
        type = "bar", marker = list(color = "#F8766D")) %>%
  add_trace(y = ~`Marriage Pressure(yes).y`, name = "Total Students",
            marker = list(color = "#00BFC4")) %>%
  layout(title = "Marriage Pressure vs Total Students by Academic Year",
         xaxis = list(title = "Academic Year"),
         yaxis = list(title = "Frequency"),
         barmode = "stack")

```

Overall, the analysis suggests that marriage pressure may have an impact on the academic decisions of students, with higher levels of marriage pressure being associated with fewer students in higher academic years.



### To determine the association between mental health and marriage pressure.

```{r}
library(dplyr)
df<- data %>%
  select(phq9) %>%
  mutate(phqcat = 
           ifelse(phq9 <= 4, 1,
                  ifelse(phq9 <= 9,2,
                         ifelse(phq9<= 14,3,
                                ifelse(phq9<= 19,4,
                                       ifelse(phq9<= 27, 5, data$phq9)))))
           )

data<- merge(data, df, by = 'phq9')

library(kableExtra)

# Execute Pearson's Chi-squared test
result <- chisq.test(data$MarriagePressure, data$phqcat)

# Create a table with the results
tbl <- data.frame(
  "Test" = "Pearson's Chi-squared test",
  "Variables" = "Marriage Pressure and phq9 Categories",
  "X-squared" = round(result$statistic, 2),
  "df" = result$parameter,
  "p-value" = format.pval(result$p.value)
) %>%
  kable(align = "c") %>%
  kable_styling(full_width = FALSE)

# Print the table
tbl


```

Here, p value < 0.05,
So, Based on the result we can conclude that there is significant relationship between Marriage Pressure and PHQ-9(Patient Health Questionnaire).




#### ------------------------------------------------------------------ The End ----------------------------------------------------------






